cardinalR: Generating interesting high-dimensional data structures

### 2025-04-17 paper-cardinalR.Rmd
Added plan for writing
Initial tabel of branching data

@@

>>>>

### Main function

### Branching

```{r}
branch_tb <- tibble(fun = c("gen_expbranches",
                             "gen_linearbranches",
                             "gen_curvybranches", 
                             "gen_orglinearbranches", 
                             "gen_orgcurvybranches"), 
                      exp = c("",
                               "", 
                               "",
                               "",
                               ""))
```

```{r branching-tb-html, eval=is_html_output()}
branch_tb |> 
  kable(caption = "cardinalR branching data generation functions", col.names = c("Function", "Explanation")) 
```

```{r branching-tb-pdf, eval=is_latex_output()}
branch_tb |> 
  kable(caption = "cardinalR branching data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

### Cone

### Cube

### Gaussian

### Linear

### Mobius

### Polynomial

### Pyramid

### S-curve

### Sphere

@@

### Odd shapes

### Additional functions
